---
title: "Simple document"
author: Linshan Xie
date: 2024-10-24
output: github_document
---

```{r}
library(ggplot2)
knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal()+theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis")

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

Load the key packages.
```{r}
library(tidyverse)
library(p8105.datasets)
```

Do some data cleaning
```{r}
data("nyc_airbnb")

nyc_airbnb = 
  nyc_airbnb |> 
  mutate(stars = review_scores_location / 2) |> 
  rename(
    borough = neighbourhood_group,
    neighborhood = neighbourhood) |> 
  filter(borough != "Staten Island") |> 
  select(price, stars, borough, neighborhood, room_type) |>
  mutate(
    borough = fct_infreq(borough),
    room_type = fct_infreq(room_type)
  )
```

## fit some models
Start relatively simple.
```{r}
fit = lm(price ~ stars, data = nyc_airbnb)

summary(fit)

names(fit)

coef(fit)

fit |>
  broom::tidy() |>
  select(term, estimate, p.value)

fit|>
  broom::glance()
```

```{r}
fit = lm(price ~ stars + borough, data = nyc_airbnb)

fit |>
  broom::tidy() |>
  select(term, estimate, p.value) |>
  mutate(
    term = str_replace(term, "borough", "Borough: ")
  ) |>
  knitr::kable(digits = 3)
```

## Some diagnostics

Backtrack to some EDA
```{r}
nyc_airbnb |>
  ggplot(aes(x = stars, y = price)) +
  geom_point() +
  stat_smooth(method = "lm")
```


Most diagnostics use residuals

```{r}
modelr::add_residuals(nyc_airbnb, fit) |>
  ggplot(aes(x = borough, y = resid)) +
  geom_violin() +
  ylim(-200, 500)
```

residuals against fitted values

```{r}
nyc_airbnb |>
  modelr::add_residuals(fit) |>
  modelr::add_predictions(fit) |>
  ggplot(aes(x = pred, y = resid)) +
  geom_point()
```

## Hypothesis testing
 
```{r}
fit_null = lm(price ~ stars + borough, data = nyc_airbnb)
fit_alt = lm(price ~ stars + borough + room_type, data = nyc_airbnb)
```

For single coefficients, look at the table

```{r}
fit |>
  broom::tidy()
```

when adding more than one coefficients, use "ANOVA"
```{r}
fit_null |> 
  broom::tidy()

fit_alt |>
  broom::tidy()

anova(fit_null, fit_alt) |>
  broom::tidy()
```

## Do effects differ aross boroughs
```{r}
nyc_airbnb |>
  lm(price ~ stars * borough + room_type * borough, data = _) |> 
  broom::tidy() |> 
  knitr::kable(digits = 3)
```

Could just fit separate models.

```{r}
nyc_airbnb |>
  filter(borough == "Manhattan") |>
  lm(price ~ stars + room_type, data = _) |>
  broom::tidy()
```

Get fancy and use list colums
```{r}
nyc_airbnb |>
  nest(data = -borough) |>
  mutate(
    model = map(data, \(x) lm(price ~ stars + room_type, data = x)),
    result = map(model, broom::tidy)
  ) |>
  select(borough, result) |>
  unnest(result) |>
  select(borough, term, estimate) |>
  pivot_wider(
    names_from = term,
    values_from = estimate
  )
```

what about room type across manhattan neighborhoods?
```{r}
nyc_airbnb |>
  filter(borough == "Manhattan",
         neighborhood == "Chinatown") |>
  lm(price ~ stars + room_type, data = _) |>
  broom::tidy()
```


Let's do this for all neighborhoods
```{r}
manhattan_neighborhood_fit_df = 
nyc_airbnb |>
  filter(borough == "Manhattan") |>
  nest(data = -(borough:neighborhood)) |>
  mutate(
    model = map(data, \(x) lm(price ~ stars + room_type, data = x)),
    result = map(model, broom::tidy)
  ) |>
  select(neighborhood, result) |>
  unnest(result)
``` 

Look at the effect of room_type
```{r}
manhattan_neighborhood_fit_df |>
  filter(str_detect(term, "room_type")) |>
  ggplot(aes(x = term, y = estimate)) +
  geom_boxplot()
```

```{r}
manhattan_neighborhood_fit_df |>
  filter(str_detect(term, "room_type")) |>
  filter(estimate > 0)
```







